\documentclass[12pt,openright,a4paper]{article}
\setlength{\parindent}{1.3cm}
\setlength{\parskip}{0.2cm}
\usepackage[alf]{abntex2cite}
\usepackage{graphicx}
\usepackage{indentfirst} 
\usepackage{lmodern}
\usepackage{listings}
\pagenumbering{arabic}
\usepackage{lineno}
\linenumbers




\begin{document}
	\linespread{1.5}
 \fontsize{16}{10}\selectfont \centering \textbf{Analysis of computer science newcomers student's motivation} \\
	\fontsize{14}{10}\selectfont {Analysis of student's motivation}\newline

\fontsize{12}{10}
\flushleft
	\textbf{Authors:}\\
	\textbf{Student name:} Felipe Augusto Ferreira de Castro\\
	\textbf{Affiliations:} Federal University of Uberlandia\\
	\textbf{Email:} felipeaugusto.ferreiradecastro@gmail.com \newline
	
\textbf{Professor name:} João Henrique de Souza Pereira\\
\textbf{affiliations:} Federal University of Uberlandia\\
\textbf{email:} joaohs@ufu.br\newline

\textbf{Number of pages:}\\
\textbf{Number of figures:}\\
\textbf{Number of tables:}\\
\textbf{Abstract word number:}\\
\textbf{introdution word number:}\\
\textbf{discussion word number:}\newline
	
\textbf{Acknowledgments}\\	
My thanks to comppet group that lent me a room to make all data collecting and to all 4 volunteers who made the project possible.\newline

\textbf{conflicts of interest}\footnote{The authors declare no competing financial interests.}

\newpage
\tableofcontents
\newpage
\section{Abstract}
Depression and other mind diseases are currently being reported at universities. Due to it, this research was proposed to observe a group of newcomer students of the Federal University of Uberlândia (UFU) along two semesters, furthermore ,using resources provided by BCI(Brain computer interface)  technology, collect data about their emotional state.

Data collecting were made on 3 points of semester and each one was proposed to volunteers do same activity related to computer science course. They executed those activites  while wearing a EEG based equipment, which was responsible for collecting their emotional data.

The results were satisfying,  students became more stressed along time and their excitement descreased.     Surprisingly relaxation has increased, different from what was expected. The other feelings had no great changes, though.

\section{Significance Statement}
\section{Introduction}
\section{Materials and Methods}
\subsection{Experimental desing and statistical Analyses}
\section{Results}
\section{Discussion}
\section{References}
\end{document}